### 2019-05-28 initial/notes.tex
check in histograms into notes

            \item $s_c > S_0$: CS4 becomes \emph{attracting}, and so two
                consequences: points initially above the separatrix are sucked
                downwards, and all encounters go to CS2 after 100\% separatrix
                entry probability.
        \end{itemize}
        Since $S_0$ is some function of $s$, it is clear that for intermediate
        values of $s_C$, we will see single separatrix hopping at early times
        while separatrix attraction at late times.
\end{itemize}

>>>>

            \item $s_c > S_0$: CS4 becomes \emph{attracting}, and so two
                consequences: points initially above the separatrix are sucked
                downwards, and all encounters go to CS2 after 100\% separatrix
                entry probability.
        \end{itemize}
        Since $S_0$ is some function of $s$, it is clear that for intermediate
        values of $s_C$, we will see single separatrix hopping at early times
        while separatrix attraction at late times.

    \item Finally, we may compare histograms of outcomes when $s_c > S_0, s_c <
        S_0$. For $s_c > S_0$, all points get attracted into CS2, which then
        synchronizes quickly; this is illustrated poorly in
        \autoref{fig:1hist07}.

        On the other hand, when $s_c < S_0$, points below CS4 only get one
        chance at hopping. We can perform similar Melnikov calculation to above
        by integrating the true tidal term $\pd{\mu^{(1)}}{t} = \epsilon\p*{1 -
        \mu^2}\p*{2\Omega_1/s - \mu}$ and find that the hopping probability
        $P_{hop} \propto \frac{\mu}{2\Omega_1/s} \propto \sqrt{s}$ or in fact
        scaling with $\eta^{-1/2}$; the difference comes in the $1/s$ dependence
        in the single-leg integral and the $-\mu$ factor in the double-leg
        integral. Thus, points closer to the initial separatrix actually should
        experience higher entry probability, also observed in
        \autoref{fig:1hist02}.

        Finally, we can somewhat see what the transition regime looks like in
        \autoref{fig:1hist03}. Points close to the separatrix experience
        attracting dynamics and all hop, while points far away from the
        separatrix experience the $\sqrt{s}$ hopping probability.
        \begin{figure}[t]
            \centering
            \begin{subfigure}{0.32\textwidth}
                \centering
                \includegraphics[width=\textwidth]{1_weaktide/1hist_0_7.png}
                \caption{Outcomes when $s_c = 0.7 > S_0$.}\label{fig:1hist07}
            \end{subfigure}
            \begin{subfigure}{0.32\textwidth}
                \centering
                \includegraphics[width=\textwidth]{1_weaktide/1hist_0_2.png}
                \caption{Outcomes when $s_c = 0.2 > S_0$.}\label{fig:1hist02}
            \end{subfigure}
            \begin{subfigure}{0.32\textwidth}
                \centering
                \includegraphics[width=\textwidth]{1_weaktide/1hist_0_3.png}
                \caption{Outcomes when $s_c = 0.3 \sim S_0$.}\label{fig:1hist03}
            \end{subfigure}
            \caption{Outcome hists.}
        \end{figure}
\end{itemize}
